\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDEs

### 2015-03-06 paper_draft1.tex
Minor syntax changes

\documentclass[12pt,leqno]{article}

@@

{\bf \abstractname{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form. The method for keeping numerical conservation at grid cell interfaces is described. The algorithm was (will be) tested for simple 1D scalar linear and non-linear problems, and to some simple systems. Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}} {\small}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=.65\textwidth]{berg-lev-fig21}
    \caption{Essential figure for flux adapting Cartesian grids. The top grid is the normal coarse grid we are used to using with fluxes indicated. The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids. Recall that $2\hat{h}=h$ and $2\hat{k}=k$. The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
    \label{fig21}
\end{figure}

@@

\section{Examples of 1D AMR}
\subsection{scalar advection}
The simplest problem (and most boring) is the 1D scalar advection equation
\begin{equation}
q(x,t)_{t} + \bar{u} q(x,t)_{x}=0
\end{equation}
where $\bar{u}$ is a constant representing the velocity of displacement. Let $\bar{u}>0$ for simplicity (right going).
The Riemann problem in this case consists of adding the initial conditions:
\begin{equation}
q(x,0):= \phi(x)=
\left\{ \begin{array}{c}
q_l , \, \, \, \, x<0\\
q_r , \, \, \, \, x>0\end{array}\right 
\end{equation}
\noindent Here the coefficient matrix is the number $\bar{u}$ which has eigenvalue $\lambda^1 = \bar{u}$ and eigenvector $r^1 =1$ and the jump discontinuity determined by $q_r - q_l$ propagates with speed $\lambda^1$ along characteristics. The solution is 
\begin{equation}
q(x,t):= \phi(x-\lambda^1 t) \, .
\end{equation}

@@

\begin{equation}
q(x,t)=\left( \begin{array}{c}
h  \\
h u\end{array} \right)
=
\begin{equation}
\left( \begin{array}{c}
q^1  \\
q^2\end{array} \right) 
\end{equation}
\noindent and

>>>>

\documentclass[11pt,leqno]{article}

@@

{\small {\bf \abstractname}{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form. The method for keeping numerical conservation at grid cell interfaces is described. The algorithm was (will be) tested for simple 1D scalar linear and non-linear problems, and to some simple systems. Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}}

@@

%\begin{figure}[h]
   % \centering
    %\includegraphics[width=.65\textwidth]{berg-lev-fig21}
   % \caption{Essential figure for flux adapting Cartesian grids. The top grid is the normal coarse grid we are used to using with fluxes indicated. The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids. Recall that $2\hat{h}=h$ and $2\hat{k}=k$. The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
    %\label{fig21}
%\end{figure}

@@

\section{Examples of 1D AMR}
\subsection{scalar advection}
The simplest problem (and most boring) is the 1D scalar advection equation
\begin{equation}
q(x,t)_{t} + \bar{u} q(x,t)_{x}=0
\end{equation}
where $\bar{u}$ is a constant representing the velocity of displacement. Let $\bar{u}>0$ for simplicity (right going).
The Riemann problem in this case consists of adding the initial conditions:
\begin{equation}
q(x,0):= \phi(x)=
\left\{ \begin{array}{c}
q_l , \, \, \, \, x<0\\
q_r , \, \, \, \, x>0\end{array}\right. 
\end{equation}

\noindent Here the coefficient matrix is the number $\bar{u}$ which has eigenvalue $\lambda^1 = \bar{u}$ and eigenvector $r^1 =1$ and the jump discontinuity determined by $q_r - q_l$ propagates with speed $\lambda^1$ along characteristics. The solution is 
\begin{equation}
q(x,t):= \phi(x-\lambda^1 t) \, .
\end{equation}

@@

\begin{equation}
q(x,t)=\left( \begin{array}{c}
h  \\
h u\end{array} \right)
=
\left( \begin{array}{c}
q^1  \\
q^2\end{array} \right) 
\end{equation}
\noindent and
